What's hot and what's not:\\Windowed developer topic analysis

### 2009-08-15 lda-experiment.tex
More expiremental stuff

>>>>

\subsection{Observations}

We ran it and we found that wordnet for correctness was too
generic. We ran it on MaxDB 7.500 with the words: integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, and reliability.

We had 500 topics extracted.
